---
title: "assignment_1"
author: "Rohin Sri Kumar"
date: "31/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(babynames)
```

## 1Q) Plot the number of male and female babies named Taylor *by year*

ans: Plotted the total males and females by overlaying them

```{r 1Q)}
names_ <- group_by(filter(babynames, name == "Taylor"))
totalbabies <- select(names_, year, sex, n)
totaltaylorbabies <- aggregate(totalbabies$n, by = list(year = totalbabies$year), FUN = sum)
ggplot(data = totaltaylorbabies, mapping= aes(year, x)) + geom_point()

```

## 2Q)Is a 16 year old named Quinn more likely to be a boy or a girl?

ans:16 years before 2017 is 2001. hence quinn is born in 2001.From the plot its more likely to be a boy

```{r 2Q)}
quinn=filter(babynames,name=="Quinn",year==2001)
ggplot(data = quinn,aes(sex,n))+geom_col()
```

## 3Q)Is a 2 year old named Quinn more likely to be a boy or a girl?

ans:2 years before 2017 is 2015. hence quinn is born in 2015.From the plot its more likely to be a girl

```{r 3Q)}
quinn2=filter(babynames,name=="Quinn",year==2015)
ggplot((data=quinn2),aes(sex,n))+geom_col()
```

## 4Q) What is your best guess as to how old a woman named Susan is?

ans: The more number of susans are from the year 1955. Now the considering the current year as 2017. The age of susan would be 62 years.(2017-1955)

```{r 4Q)}
sussan=filter(babynames,name=="Susan")
ggplot(data=sussan,aes(year,n))+geom_col()+geom_text(aes(label= year), check_overlap = FALSE, color= "black", size=2.5)

```