---
title: "donga_ard224_assignment3"
author: "Rohin Donga"
date: "2/13/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r cars}
library(tidyverse)
library(Lahman)
master_table <- Lahman::People
master_group <- master_table %>% group_by(birthYear) %>% count(birthYear, nameFirst) %>% mutate(prop = n/sum(n))
master_group

#Loaded the tidyverse and Lahman packages, then imported the Master table and converted it into a dataframe. Next, I grouped the Master table by birth year and obtained the number of names for each birth year. Finally, I created a new column named "prop" by calculating the proportion of names for each birth year, which is obtained by dividing the number of names by the sum of all names.
```

## Problem 2

```{r}
master_group %>% filter(str_detect(nameFirst, "^Y"))

#Applied a regular expression (regex) filter to select only the rows in a dataset where the first name of the individual starts with the letter "Y".
```

##Problem 3

```{r}
master_group %>% filter(str_detect(nameFirst, "[aeiou]{3}"))

#Used a bracketed regular expression (regex) filter to select only the rows in a dataset that contain vowels. Additionally, I added "{3}" to the regex pattern to specify that the selected rows must have at least three consecutive vowels in their content.
```

##Problem 4

```{r}
library(lubridate)
master_table2 <- master_table %>% mutate(birthYear2 = year(birthDate))

#Created a new table by extracting the year from the "birthDate" column of an existing dataset and stored it in a new column named "birthYear2".
```

#Number of NAs in birthYear

```{r}
master_table2 %>% filter(is.na(birthYear)) %>% count(birthYear) %>% select(n)

#Filter by na values, get count and select as n
```

114 NAs in birthYear

#Number of NAs in birthYear2

```{r}
master_table2 %>% filter(is.na(birthYear2)) %>% count(birthYear2) %>% select(n)

#Filter by na values, get count and select as n
```

423 NAs in birthYear2 

#Number of NAs in birthYear and birthYear2

```{r}
master_table2 %>% filter(is.na(birthYear) & is.na(birthYear2)) %>% count(birthYear) %>% select(n)

#Filter by na values in both columns, get count and select as n
```

114 NAs in birthYear and birthYear2

#Check for matching cases among entries with no NA for either birthYear or birthYear2

```{r}
nona_master_table <- master_table2 %>% filter(!is.na(birthYear) & !is.na(birthYear2)) 
nona_master_table %>% nrow()

#filter by both columns not being na, select the number of rows to get the total entries
```

19670 rows for no NAs in either column

```{r}
nona_master_table %>% filter(birthYear == birthYear2) %>% nrow()

#filter by birthYear equaling birthYear2, get number of rows
```

19670 rows where the year is the same in both columns

All the remaining cases match!

##Problem 5

```{r}
joined_table <- inner_join(master_table, Lahman::Fielding, by="playerID")
career_games <- joined_table %>% group_by(playerID, nameFirst, nameLast, nameGiven) %>% summarise(G = sum(G))

#perform an inner join on the Master/Fielding tables, obtain desired table by selecting playerID, nameFirst, nameLast and nameGiven, then summarise games by the sum of games over this grouping
```

##Problem 6

```{r}
career_games <- career_games %>% mutate(fullname = paste(nameFirst, nameLast, " "))

#Used paste command to paste the first and last names together, separated by a space
```

##Problem 7

```{r}
five_most_popular_names <- career_games %>% filter(G >= 500) %>% group_by(nameFirst) %>% count(nameFirst) %>% arrange(desc(n)) %>% head(5)
five_most_popular_names
#First, filter for players who played at least 500 games, then group by + count first names, arrange in descending order, and obtain the first five
```

```{r}
master_group %>% filter(nameFirst %in% five_most_popular_names$nameFirst) %>% ggplot(aes(birthYear,n)) + ggtitle("MLB First Names over time") + ylab("Frequency") + theme(plot.title = element_text(size=10, hjust = 0.5)) + geom_path(aes(colour = nameFirst))
```


