---
title: "donga_ard224_assignment8"
author: "ROHIN SRI KUMAR"
date: "04/23/2023"
output: html_document
---
```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(tidytext)
library(textdata)
library(rvest)
library(httr)
library(curl)
library(jsonlite)
library(modelr)
library(ggbeeswarm)
library(magrittr)
library(igraph)
library(sna)
library(GGally)
library(intergraph)
library(choroplethr)
library(choroplethrMaps)
library(stringi)
library(tidycensus)
```

# Problem 1

# 1

```{r}
gap_nested <- gapminder %>% group_by(country, continent) %>% nest()
head(gap_nested)
```


```{r}
gap_lm <- gap_nested %>% mutate(model = map(data, ~lm(log10(gdpPercap) ~ year, data = .)))
head(gap_lm)
```

# 2

```{r}
gap_lm_residual <- gap_lm %>% mutate(resid = map2(data, model, add_residuals)) %>% unnest(resid)
head(gap_lm_residual)
```


```{r}
gap_lm_residual %>% ggplot(aes(year, resid)) + geom_line(aes(group = country)) + geom_smooth(color="orange") + ggtitle("each country residuals")

gap_lm_residual %>% ggplot(aes(year, resid)) + geom_line(aes(group = country)) + geom_smooth(color="orange") + facet_wrap(~continent) + ggtitle("each continents residuals")
```

# 3

```{r}
gap_lm_clean <- gap_lm %>% mutate(tidy = map(model, tidy))
gap_lm_clean %>% mutate(tidy = map(tidy, ~filter(., term == "year"))) %>% unnest(tidy) %>% ggplot(aes(continent, estimate)) + geom_boxplot() + geom_beeswarm() + ggtitle ("continent wise slope coefficient value")
```

we can observer for the graph that europe has symmertric rate of growth where as in asia some have positive growth while others have negative growth of gdp.

```{r}
gap_lm_clean %>% mutate(tidy = map(tidy, ~filter(., term == "year"))) %>% unnest(tidy) %>% ggplot(aes(continent, statistic)) + geom_boxplot() + geom_beeswarm() + ggtitle("continent wise t-statistic")
```

if we observer the plot the african countries arent stable where as for the rest of the continents we can say that year is plays a major role for the model. 

#4

```{r}
dec_gdp <- gap_lm_clean %>% mutate(tidy = map(tidy, ~filter(., term == "year"))) %>% unnest(tidy) %>% filter(estimate < 0 & p.value < 0.05) %>%
  ungroup() %>% select(country, estimate, p.value)
dec_gdp
```

the interpretation of the linear model fit for these countries is that as the time increases the gdppercaptia is decreasing.

#5

```{r}
gapminder %>% filter(country %in% dec_gdp$country) %>% group_by(country, continent) %>% ggplot(aes(x = year, y = log10(gdpPercap), color = country)) + geom_line()
```

# Problem 2

```{r}
mtcrs <- mtcars %>% crossv_kfold(k = 8)
mtcrs
```

```{r}
mtnls <- mtcars %>% nls(mpg ~ k / wt + b, ., start = list(k = 1, b = 0))
mtnls
```

```{r}
mtlm <- mtcars %>% lm(mpg ~ wt, .)
mtlm
```

```{r}
mtcrsrsme_1 <- mtcrs %>% mutate(model = map(train, ~nls(mpg ~ k/wt+b, data = .$data, start = list(k = 1, b = 0))))
mtcrsrsme_1%$% map2_dbl(model, test, rmse) %>%  mean()
```


```{r}
mtcrsrsme_2 <- mtcrs %>% mutate(model = map(train, ~lm(mpg ~ wt, data = .)))
mtcrsrsme_2 %$% map2_dbl(model, test, rmse) %>% mean()
```

***********We can conclude from rsme that the linear model fits better than non-linear model. 


# Problem 3

##1

```{r}
nodes <- read.csv("/Users/rohin/Desktop/sunbelt2021/Data files/Dataset1-Media-Example-NODES.csv", header=TRUE, as.is=TRUE)
links <- read.csv("/Users/rohin/Desktop/sunbelt2021/Data files/Dataset1-Media-Example-EDGES.csv", header=TRUE, as.is=TRUE)
network_graph <- graph_from_data_frame(d=links, vertices = nodes, directed = TRUE)
network_graph
```

# 2

```{r}
network <- asNetwork(network_graph)
network
```

# 3
```{r warning=FALSE}
ggnet2(network, size = "audience.size", color = "media.type", arrow.size=5, arrow.gap=0.025)
```

# 4

```{r}
mean(degree(network, gmod='digraph'))
density_n_nw <- network %>% network.density()
density_n_nw
```

# Problem 4

```{r}
url <- "https://www.worldometers.info/world-population/population-by-country/"
pop_by_country <- url %>% read_html() %>% html_nodes("table") %>% html_table(fill = TRUE) %>% .[[1]]
head(pop_by_country)
```

# 1

```{r warning=FALSE}
pop_by_country <- pop_by_country %>%
  rename(`region` = `Country (or dependency)`, `value` = `Density (P/Km²)`) %>%
  mutate(`region` = tolower(`region`),`Population (2020)` = as.integer( str_replace_all(.$`Population (2020)`, ",", "")),
         `Yearly Change` = as.double(str_replace_all(.$`Yearly Change`, " %", "")),
         `Net Change` = as.integer(str_replace_all(.$`Net Change`, ',', '')),
         `value` = as.integer(str_replace_all(.$`value`, ',', '')),
         `Land Area (Km²)` = as.integer(str_replace_all(.$`Land Area (Km²)`, ',', '')),
         `Migrants (net)` = as.integer(str_replace_all(.$`Migrants (net)`, ',', '')),
         `Fert. Rate` = as.double(`Fert. Rate`),
         `Med. Age` = as.integer(`Med. Age`),
         `Urban Pop %` = as.integer(str_replace_all(.$`Urban Pop %`, ' %', '')),
         `World Share` = as.double(str_replace_all(.$`World Share`, ' %', ''))
         )

head(pop_by_country)

```

# 2

```{r}
pop_by_country_cmap <- pop_by_country %>%
  mutate(region = replace(region, region == 'united states', 'united states of america')) %>%
  mutate(region = replace(region, region == 'north macedonia', 'macedonia')) %>%
  mutate(region = replace(region, region == 'serbia', 'republic of serbia')) %>%
  mutate(region = replace(region, region == 'timor-leste', 'east timor')) %>%
  mutate(region = replace(region, region == 'tanzania', 'united republic of tanzania')) %>%
  mutate(region = replace(region, region == 'bahamas', 'the bahamas')) %>%
  mutate(region = replace(region, region == 'côte d\'ivoire', 'ivory coast')) %>%
  mutate(region = replace(region, region == 'dr congo', 'democratic republic of the congo')) %>%
  mutate(region = replace(region, region == 'congo', 'republic of congo')) %>%
  mutate(region = replace(region, region == 'czech republic (czechia)', 'czech republic')) %>%
  mutate(region = replace(region, region == 'guinea-bissau', 'guinea bissau')) %>%
  mutate(region = replace(region, region == 'czech republic (czechia)', 'czech republic'))
```

```{r warning=FALSE}
country_choropleth(pop_by_country_cmap)
```

# 3

```{r}
data(country.regions)
setdiff(country.regions$region, pop_by_country_cmap$region)
```

# 4

```{r}
sort(setdiff(pop_by_country_cmap$region, country.regions$region))
```
# We can see from the results that these countries do not overlap, thus the cleaning is appropriate, and the map is satisfactory.

# Problem 5

# 1
```{r, Warning = FALSE}
census_api_key("bd96ae2127452afc80ec5b87e4a652d99c7a2c57", install = TRUE, overwrite = TRUE)
```

```{r}
median_income <- get_acs(geography = "tract", variables = c(medincome = "B19013_001"), year = 2020, state="NJ")

median_rent <- get_acs(geography = "tract", variables = c(medrental = "B25064_001"), year=2020, state="NJ")

combined_median <- median_rent %>% mutate(income=median_income$estimate) %>% select(-variable) %>% select(-moe) %>% rename(rent=estimate)

head(combined_median)
```


```{r}
combined_median %>% ggplot(aes(income, rent)) +geom_point() + ggtitle("rent vs income")
```



# We can see from the graph that the relationship between median income and rent is not linear.


# 2

```{r}
combined_median_lm <- combined_median %>% lm(rent ~ income, .)
summary(combined_median_lm)
```


```{r}
combined_median %>% add_predictions(combined_median_lm, var = "pred") %>% ggplot(aes(income, rent)) + geom_point() + geom_line(aes(income, pred , color = 'model'))+ scale_color_manual(values=c('orange'))
```



```{r}
better_combined_median <- combined_median %>% lm(rent ~ log10(income)+income, .)
summary(better_combined_median)

```

```{r}
combined_median %>% add_predictions(better_combined_median) %>% ggplot() + geom_point(aes(income, rent)) + geom_line(aes(income, pred), color = 'orange')
```
# In the second model, R2 has improved.

# 4


```{r}
median_rent_11_15 <- get_acs(geography = "county", variables = c(medrental = "B25064_001"), year = 2020, state = "NJ")
  
median_rent_15_20 <- get_acs(geography = "county", variables = c(medrental = "B25064_001"), year = 2015, state = "NJ")

```


```{r}
nj_rental_15 <- median_rent_11_15 %>%select(-variable) %>%select(-moe) %>%rename(rent_20 = estimate)
nj_rental_20 <- median_rent_15_20 %>%select(-variable) %>%select(-moe) %>%rename(rent_15 = estimate)
nj_rental_15_20 <- inner_join(nj_rental_20, nj_rental_15)

nj_rental_15_20 <- nj_rental_15_20 %>% mutate(Percentage_Change = rent_20/rent_15)
head(nj_rental_15_20)
```


```{r}
nj_rental_15_20 %>% mutate(NAME = str_replace_all(NAME, " County, New Jersey", "") ) %>% ggplot(aes(x = reorder(NAME, Percentage_Change), y = Percentage_Change)) +
  geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + xlab("County")+ylab("Percentage Change")+ggtitle ("percentage change of rent for each county in a newjersey")
```